The imprint of global magma oceans on exoplanet demographics

### 2022-08-06 src/tex/ms.tex
change title
add SAG13 planetary sample and some notes

% Define document class
\documentclass[twocolumn]{aastex631}

@@

% Title
\title{An open source scientific article about extrasolar magma oceans}

@@

% Main body
\section{Introduction}
\Blindtext[4]

@@

>>>>

% Define document class
%\documentclass[twocolumn]{aastex631}
\documentclass[modern]{aastex631}

@@

% Title
\title{The imprint of global magma oceans on exoplanet demographics}

@@

% Main body
\section{Introduction}
Several patterns in the planetary parameter space have been reported in demographic studies or predicted from planet formation theories.
\begin{note}
    ...long-term goal/overarching objective: derive the geophysical history of rocky extrasolar planets.
   ...
\todo[inline]{introduce magma oceans and their influence on planetary radii~\citep{Dorn2021}.}
    ...current/future observations of planets that are currently in the runaway greenhouse phase may constrain properties of their planetary mantles... make connection between interior and atmospheres.
\end{note}

@@

\section{Testing the magma ocean hypothesis}
\todo[inline]{"Methods Section" of the hypothesis testing part. Introduce the idea of constraining magma ocean frequencies and/or physics with Bayesian stats on exoplanet population; introduce Bioverse; report methods of the hypothesis tests.}

\subsection{Synthetic star and planet sample}
\subsubsection{Stellar sample from Gaia DR3}
\todo{Which star sample was actually used?}

\subsubsection{Planetary sample from SAG~13}
\todo[inline]{What is the source of our occurrence rate density from which we draw? We could also use a generative model that directly approximates an observed or theoretical density \citep[e.g.,][]{Schlecker2021b}.}
\begin{note}
    The NASA Exoplanet Program Analysis Group chartered Science Analysis Group 13 (SAG 13)...
    The inferred occurrence rate density can be expressed as a power law in planet radius and period
    \begin{equation}
        \frac{\partial^2n}{\partial \log R \, \partial \log P} = \Gamma R^{\alpha} P^{\beta}
    \end{equation}
that is broken in planet radius, resulting in the free parameters $\Gamma$, $\alpha$, $\beta$, and a breakpoint radius $R_\mathrm{break}$.
\end{note}
